Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-30 draft/paper1_rachel.tex
Edit mden profile result 2

    Most previous studies have often focused on surface brightness profiles instead 
    of mass density profiles.  
    Results can also depend on the stacking technique or the model used to extract 
    the profile (e.g., \citealt{Tal2011, DSouza2015}). 
    \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$) based on relatively 
    shallow images from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}).  
    This sample is at very low redshift ($z<0.02$), and so the \mden{} profiles from 
    \citet{Huang2013a} galaxies are accurate to smaller scales (down to $r=1$ kpc) 
    than our HSC ones.  
    Our \mden{} profiles show good agreement with the \citet{Huang2013a} sample in the radial range of overlap (out to 50 kpc). CGS images are deeper than SDSS images in the $r$-band, but the median 
    profiles from \citet{Huang2013a} still only reach to ${\sim} 50$ kpc for $z{\sim} 0$ (PUT THE EXACT REDSHIFTS HERE)
    massive galaxies.
    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
    for $z{\sim} 0.4$ galaxies out to at least 100 kpc.

    \citet{Patel2013} extracted a median \mden{} profile for massive ETGs at 
    $0.25 < z < 0.50$ using stacked \textit{HST}/ACS images. 
    These galaxies are selected at a constant cumulative number density and are 
    thought to be the progenitors of $z=0$ massive ETGs (e.g. \citealt{Leja2013}).  
    The median \mstar{} of the \citet{Patel2013} sample is 
    ${\sim} 10^{11.2} M_{\odot}$ which is lower than our lowest mass bin. 
    However, \citet{Patel2013} use the BC03 SSP model which provides masses that are roughly 0.1 dex 
    lower than our FSPS masses (Appendix~\ref{app:sed}). 
    Furthermore, the \citet{Patel2013} images are shallower than ours meaning 
    that their masses will be lower than ours because of missing light in the 
    outskirts. 
    Given these two considerations, it is reasonable to roughly compare the 
    \citet{Patel2013} profile with the one in our lowest stellar mass bin. 
    The superb resolution of the \textit{HST}/ACS image means that the profiles in
    \citet{Patel2013} can be measured down to 1 kpc. 
    The good agreement between our profiles and the ones derived from HST imaging demonstrates that our profiles are robust at $r > 3$ kpc and that we can accurately 
    measure \minn{}.

@@

%% ------------------------------------------------------------------------------------ %% 
	%Aforementioned results only use the 1-D \mden{} profiles that are baed on single 
	%band image and the flux-weighted isophotal shape, while more useful information 
	%can be gathered from the HSC images of these massive galaxies.
    So far, we have focused only on 1-D \mden{} profiles. We now consider ellipticity and $k$-corrected optical color profiles.
	We extract ellipticity profiles using \texttt{Ellipse} by leaving the shape of each isophote as a free parameter. We also apply the isophotal information derived in the $i$-band directly to other 
	filters and extract 1-D $g-r$ and $g-i$ color profiles. We apply the Galactic extinction correction and the \texttt{iSEDFit} $k$-correction  to the color profiles. Smearing by the PSF wil l make the central isophotal shape rounder than the 
	real value, while seeing differences between filters will bias the central 
	color\footnote{Since the HSC $i$-band always has better seeing, the central color 
	will become redder is seeing effects are not accounted for}. On large scales, it is more difficult to extract reliable ellipticity and 
	color profiles out to 100 kpc: at low surface brightness levels, the isophotal shape 
	becomes unstable and is easily affected by contamination. Color profiles are also more difficult to extract out to large radial scales because  getting the color accurately depends on the background subtraction and the noise levels in both bands. In this paper, we will focus on the median ellipticity and color profiles between 
	8--60 kpc where we can safely ignore the issues described above.

	The ellipticity of the isophotes contains information about the 3-D geometry 
	(e.g. \citealt{Tremblay1995, Tremblay1996, Chang2013, RodriguezPadilla2013, 
	Mitsuda2017}) and kinematics (e.g. \citealt{Cappellari2012, Weijmans2014}) of 
	stars in massive galaxies.  
	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
	massive galaxies and highlights the median profiles for the same three \mtot{} 
	bins used in Fig \ref{fig:avg_prof}.  Our results are also compared with previous work based on image stacking techniques (the PSF-removed $i$-band results from \citealt{Tal2011},  and
concentrated galaxies with $11.0<$\logms{}$<11.4$ from \citealt{DSouza2015}).
	As expected, ellipticity profiles from image stacking methods yield results that are more shallow than when  ellipticities can be measured on a galaxy-by-galaxy basis. Uncertainties in how to align galaxies, and the intrinsic isophotal twist can lead to this effect.

	In general, we find that the ellipticities of massive galaxies slowly increase with radius. This trend can even be seen directly "by eye" in HSC images (e.g. Fig \ref{fig:sdss_compare}). More interestingly, the ellipticity profiles vary with  \mtot{}: 
	at ${\sim} 10$ kpc, the median ellipticity ($< 0.2$) is similar for all three redshift bins,  but the ellipticity of the outer stellar halo increases with galaxy mass. Galaxies with  \logms{}$>11.8$ have median ellipticity profiles that become steeper at $>10$ kpc. The ellipticity of the outer profiles steadily increases from $e\le 0.2$ to $e{\sim} 0.4$ at 50-60 kpc.

	This is consistent with studies of nearby massive galaxies, both from 1-D 
	ellipticity profiles and 2-D modeling results \citep{Porter1991, Gonzalez2005, 
	Zibetti2005, Spavone2017, Huang2013a, Oh2017}. However,  to the best of our knowledge, our HSC results are the first to show  clear evidence that:  a) the ellipticities of the stellar halo  depend strongly on galaxy mass, and b)  the ellipticity of the stellar halo is anti-correlated with the slope of \mden{}.

	If accreted stars dominate the stellar halos of massive galaxies, this 
	mass-dependent ellipticity profile may contain clues about the assembly history of massive galaxies (e.g. average time since last merger, 
	average merger mass ratio).
	Previous simulations often focused on reproducing the rounder average shape 
	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), and the 
	projected ellipticity profiles and their correlations with the kinematic of 
	stars and merging history have not been well explored.

    Regarding the color profiles, it is well known that massive elliptical galaxies 
    have shallow and negative color gradients that reflect radial variations in their  
    stellar populations (e.g.\ \citealt{Carollo1993, LaBarbera2012}) and hence contain
    information about the assembly history of their stellar halos (e.g. 
    \citealt{Hirschmann2015}). 
    The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $g-r$ and 
    $g-i$ color profiles for all galaxies in our sample, together with the median profiles in three \mtot{} bins. We find the the  median $g-r$ and $g-i$ color  decreases  at larger radii, but there does not appear to be an significant mass dependence in the  gradient of the color profiles. We also compare our results with the stacked color profiles from  \citealt{LaBarbera2010}\footnote{We use the median color profiles of high-mass 
    ETGs; the original profile is in units of $R_{\mathrm{e}}$, we use a typical 
    $R_{\mathrm{e}}=8.0$ kpc to convert it into physical kpc.} and 
    \citealt{DSouza2014}.
    The median color profiles from HSC images are systematically steeper than the 
    stacked SDSS ones. 
    Considering differences in the response curves between HSC and SDSS filters, together with the uncertainties of color measurements, the HSC $(g-r)$ color profiles are  in fairly good agreement with  those from SDSS. However, the $(g-i)$ profiles of HSC galaxies are steeper compared to SDSS. The SDSS $i$-band suffers from the so-called ``red-halo'' effect
    (e.g. \citealt{Wu2005}, \citealt{Tal2011}).  This is due to  the fact that the SDSS $i$-band PSF has more prominent wing than other bands. Because the PSF model does not capture these wings, this artificially distributes more flux to the outskirts, and leads to apparently redder colors in 
    the low surface brightness outskirts of galaxies. Because HSC uses thick CCDs, HSC $i$-band images do not suffer from this effect and can be used to determine galaxy colors with higher accuracy.

@@

    In this paper, we have used  data from the HSC survey that is both simultaneously deep and wide to trace the stellar mass distributions of 
    $0.3 < z < 0.5$ massive galaxies out to $>100$ kpc and to reveal the mass-dependent nature 
    of their stellar halos.
    Here we briefly discuss the scientific implications of our results .

>>>>

    Most previous studies have often focused on surface brightness profiles instead 
    of mass density profiles.  
    Results can also depend on the stacking technique or the model used to extract 
    the profile (e.g., \citealt{Tal2011, DSouza2015}). 
    \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$) based on relatively 
    shallow images from the Carnegie-Irvine Galaxy Survey 
    (CGS, \citealt{CGS1})\footnote{https://cgs.obs.carnegiescience.edu/CGS/Home.html}.  
    This sample is at very low redshift ($z<0.02$), and so the \mden{} profiles from 
    \citet{Huang2013a} galaxies are accurate to smaller scales (down to $r=1$ kpc) 
    than our HSC ones.  
    Our \mden{} profiles show good agreement with the \citet{Huang2013a} sample in 
    the radial range of overlap (out to 50 kpc). 
    CGS images are deeper than SDSS images in the $r$-band, but the median 
    profiles from \citet{Huang2013a} still only reach to ${\sim} 50$ kpc for 
    $z<0.02$ massive galaxies.
    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
    for $z{\sim} 0.4$ galaxies out to at least 100 kpc.

    \citet{Patel2013} extracted a median \mden{} profile for massive ETGs at 
    $0.25 < z < 0.50$ using stacked \textit{HST}/ACS images. 
    These galaxies are selected at a constant cumulative number density and are 
    thought to be the progenitors of $z=0$ massive ETGs (e.g. \citealt{Leja2013}).  
    The median \mstar{} of the \citet{Patel2013} sample is 
    ${\sim} 10^{11.2} M_{\odot}$ which is lower than our lowest mass bin. 
    However, \citet{Patel2013} uses the BC03 stellar population model which leads to 
    \mstar{} that are roughly 0.1 dex lower than our FSPS estimates 
    (see Appendix~\ref{app:sed}). 
    Furthermore, the \citet{Patel2013} images are shallower than ours which means 
    that their \mstar{} could still be underestimated due to missing light in the 
    outskirts. 
    Given these two considerations, it is reasonable to roughly compare the 
    \citet{Patel2013} profile with the one in our lowest \mtot{} bin. 
    The superb resolution of the \textit{HST}/ACS image allows \citet{Patel2013} to 
    accurately measure \mden{} profile down to 1 kpc without worrying the smearing 
    effect of seeing. 
    The good agreement between our profiles and the ones derived from HST imaging 
    demonstrates that our profiles are robust at $r\geq 3$ kpc so that we can 
    accurately measure \minn{}.

@@

%% ------------------------------------------------------------------------------------ %% 
	%Aforementioned results only use the 1-D \mden{} profiles that are baed on single 
	%band image and the flux-weighted isophotal shape, while more useful information 
	%can be gathered from the HSC images of these massive galaxies.
    So far, we have focused only on 1-D \mden{} profiles. 
    We now consider ellipticity and $k$-corrected optical color profiles.
	We extract ellipticity profiles using \texttt{Ellipse} by leaving the shape of 
	each isophote as a free parameter. 
	We also apply the isophotal information derived in the $i$-band directly to other 
	filters and extract 1-D $g-r$ and $g-i$ color profiles.
	We apply the Galactic extinction correction and the \texttt{iSEDFit} $k$-correction 
	to the color profiles. 
	Smearing effect of seeing will make the central isophotal shape rounder than the 
	real value, while seeing differences between filters will bias the central 
	color\footnote{Since the HSC $i$-band always has better seeing, the central color 
	will become redder is seeing effects are not accounted for}. 
	On large scales, it is more difficult to extract reliable ellipticity and 
	color profiles out to 100 kpc: at low surface brightness levels, the isophotal 
	shape becomes unstable and is easily affected by contamination. 
	Color profiles are also more difficult to extract out to large radial scales
	because  getting the color accurately depends on the background subtraction and 
	the noise levels in both bands. 
	In this paper, we will focus on the median ellipticity and color profiles between 
	8--60 kpc where we can safely ignore the issues described above.

	The ellipticity of the isophotes contains information about the 3-D geometry 
	(e.g. \citealt{Tremblay1995, Tremblay1996, Chang2013, RodriguezPadilla2013, 
	Mitsuda2017}) and kinematics (e.g. \citealt{Cappellari2012, Weijmans2014}) of 
	stars in massive galaxies.  
	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of 
	massive galaxies and highlights the median profiles for the same three \mtot{} 
	bins as used in Fig \ref{fig:avg_prof}.  
	Our results are also compared with previous work based on image stacking techniques 
	(the PSF-removed $i$-band results from \citealt{Tal2011}, and
    concentrated galaxies with $11.0<$\logms{}$<11.4$ from \citealt{DSouza2015}).
	As expected, ellipticity profiles from image stacking methods yield results that 
	are more shallow than when ellipticity can be measured on a galaxy-by-galaxy basis.     
	Uncertainties in how to align galaxies, and the intrinsic isophotal twist can 
	lead to this effect.

	In general, we find that the ellipticities of massive galaxies slowly increase 
	with radius. 
	This trend can even be seen directly "by eye" in HSC images (e.g. 
	Fig \ref{fig:sdss_compare}). 
	More interestingly, the ellipticity profiles vary with \mtot{}: 
	at ${\sim} 10$ kpc, the median ellipticity ($< 0.2$) is similar for all three 
	redshift bins, but the ellipticity of the outer stellar halo increases with 
	\mtot{}. 
	Galaxies with \logmtot{}$>11.8$ have median ellipticity profiles that become 
	steeper at $>10$ kpc. 
	The ellipticity of the outer profile steadily increases from 
	$e\le 0.2$ to $e{\sim} 0.4$ at 50-60 kpc.

	This is consistent with studies of nearby massive galaxies, both from 1-D 
	ellipticity profiles and 2-D modeling results \citep{Porter1991, Gonzalez2005, 
	Zibetti2005, Spavone2017, Huang2013a, Oh2017}. 
	However, to the best of our knowledge, our HSC results are the first to show 
	clear evidence that:  
	a) the ellipticity of stellar halo in massive ETGs depends strongly on 
	\mstar{}, and 
	b) the ellipticity of the stellar halo is anti-correlated with the slope of 
	\mden{}.

	If accreted stars dominate the stellar halos of massive galaxies, this 
	mass-dependent ellipticity profile may contain clues about the assembly history 
	of massive galaxies (e.g. average time since last merger, average merger 
	mass ratio).
	Previous simulations often focused on reproducing the rounder average shape 
	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), and the 
	projected ellipticity profiles and their correlations with the kinematic of 
	stars and merging history have not been carefully explored.

    Regarding the color profiles, it is well known that massive elliptical galaxies 
    have shallow and negative color gradients that reflect radial variations in their  
    stellar populations (e.g.\ \citealt{Carollo1993, LaBarbera2012}) and hence contain
    information about the assembly history of their stellar halos (e.g. 
    \citealt{Hirschmann2015}). 
    The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $(g-r)$ and 
    $(g-i)$ color profiles for all galaxies in our sample, together with the median 
    profiles in three \mtot{} bins. 
    We find the the median rest-frame $(g-r)$ and $(g-i)$ color decreases at 
    larger radii, but there does not appear to be an significant \mstar{} dependence 
    in the gradient of rest-frame optical colors. 
    We also compare our results with the stacked color profiles from  
    \citealt{LaBarbera2010}\footnote{We use the median color profiles of high-mass 
    ETGs; the original profile is in units of $R_{\mathrm{e}}$, we use a typical 
    $R_{\mathrm{e}}=8.0$ kpc to convert it into physical kpc.} and 
    \citealt{DSouza2014}.
    The median color profiles from HSC images are systematically steeper than the 
    stacked SDSS ones. 
    Considering differences in the response curves between HSC and SDSS filters, 
    together with the uncertainties of color measurements, the HSC $(g-r)$ color 
    profiles are in fairly good agreement with those from SDSS. 
    However, the $(g-i)$ profiles of HSC galaxies are steeper compared to SDSS. 
    The SDSS $i$-band suffers from the so-called ``red-halo'' effect
    (e.g. \citealt{Wu2005}, \citealt{Tal2011}).  
    This is due to the fact that the SDSS $i$-band PSF has more prominent wing 
    than other bands. 
    Because the PSF model does not capture these wings, this artificially distributes 
    more flux to the outskirts, and leads to apparently redder colors in the low 
    surface brightness outskirts of galaxies. 
    Because HSC uses thick CCDs, HSC $i$-band images do not suffer from this effect 
    and can be used to determine galaxy colors with higher accuracy.

@@

    In this paper, we have used data from the HSC survey that is both simultaneously 
    deep and wide to trace the stellar mass distributions of $0.3 < z < 0.5$ massive 
    galaxies out to $>100$ kpc and to reveal the mass-dependent nature of their 
    stellar halos.
    Here we briefly discuss the scientific implications of our results.
